LSOA domestic Electricty and Gas maps

### 2021-08-24 LSOA domestic Elec and Gas.Rmd
Fixed errors in LSOA dom elec and gas

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_sf_de20102019, LSOA11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill= de_diff)) +
  scale_fill_continuous(name = "Change in Mean consumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom gas 
```{r Creating the dfference in LSOA dom gas consumption variable}
#Green indicates a decrease in gas consumption from 2010 to 2019
#Red indicates an increase in gas consumption from 2010 to 2019
dgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))
dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$`Mean consumption (kWh per meter)`
dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$`Mean consumption (kWh per meter)`
merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
names(merged_dgas)
merged_dgas$dg_diff<-as.numeric(merged_dgas$dgas2019) - merged_dgas$dgas2010
summary(merged_dgas)
```

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(merged_dgas) +
  geom_sf(aes(fill=dg_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```

#####Cities in more detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill= de_diff)) +
  scale_fill_continuous(name = "Change in Mean consumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = de_diff)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = de_diff)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference between 2010 and 2019 dom gas 
```{r Creating the dfference in LSOA dom gas consumption variable}
#Green indicates a decrease in gas consumption from 2010 to 2019
#Red indicates an increase in gas consumption from 2010 to 2019
dgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))

dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$'Mean consumption (kWh per meter)'
dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$'Mean consumption (kWh per meter)'
merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Lower Layer Super Output Area (LSOA) Code", all = TRUE)
names(merged_dgas)
merged_dgas$dg_diff<-as.numeric(merged_dgas$dgas2019) - merged_dgas$dgas2010
summary(merged_dgas)
```

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```

#####Cities in more detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Southampton")

# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = dg_diff)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Gas}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Portsmouth")

# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = dg_diff)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Winchester")

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = dg_diff)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
